Probabilistic Forecast Reconciliation

### 2018-06-05 Presentation/ProbForeRec.tex
changes to presentation

\usepackage{amsmath,amsthm, bm, tikz}

@@

  picture of hierarchy  

@@

  	    {\bm S}=\begin{pmatrix} 1 &1 \\1 &0 \\0 &1 \\

@@

@@

    This definition is not unique, it could be defined as the span of: 
    {\bm S}^*=\begin{pmatrix}1&0\\0&1\\1&-1\end{pmatrix}

@@

    Let $(\mathbb{R}^m,\mathcal{F}_{\mathbb{R}^m},\nu)$ and $(\mathfrak{s},\mathcal{F}_{\mathfrak{s}},\nu_\mathfrak{s})$ be probability triples on $m$-dimensional space and the coherent subspace respectively.

@@

      \nu(\mathcal{B})=\nu_{\mathfrak{s}}(s(\mathcal{B}))\quad\forall\mathcal{B}\in \mathcal{F}_{\mathcal{R}_m}

@@

  	\tilde{\nu}(s(\mathcal{B}))=\nu(\mathcal{B})=\hat{\nu}(g^{-1}(\mathcal{B}))\quad\forall \mathcal{B}\in\mathbb{R}^n

@@

   		    	\item Reconiliation is better than no reconciliation.

>>>>

\usepackage{amsmath,amsthm, bm, tikz,qtree}

@@

\begin{figure}
	\begin{center}
		\leaf{AA} \leaf{AB} 
		\branch{2}{A}
		\leaf{BA} \leaf{BB}
		\branch{2}{B}
		\branch{2}{Tot}
		\qobitree
	\end{center}
\end{figure}

@@

  	    {\bm S}=\begin{pmatrix} 1 &1 &1 &1 \\1 &1 &0 &0 \\0 &0 &1 &1 \\ &{\bm I_{4\times 4}}

@@

  \begin{frame}{Geometry: Oblique Projection}
  	\vspace{-0.9cm}
  	\input{Figs/pointforerec_schematic}

@@

    Instead of using bottom-level series a different combination of $m$ {\bf basis series} could be used (e.g. top and $m-1$ bottom).  Although ${\bm S}$ would be different $\mathfrak{s}$ would be the same.

@@

    Let $(\mathbb{R}^m,\mathcal{F}_{\mathbb{R}^m},\nu)$ and $(\mathfrak{s},\mathcal{F}_{\mathfrak{s}},\mu)$ be probability triples on $m$-dimensional space and the coherent subspace respectively.

@@

      \nu(\mathcal{B})=\mu(s(\mathcal{B}))\quad\forall\mathcal{B}\in \mathcal{F}_{\mathcal{R}_m}

@@

  	\tilde{\nu}(s(\mathcal{B}))=\nu(\mathcal{B})=\hat{\nu}(g^{-1}(\mathcal{B}))\quad\forall \mathcal{B}\in\mathcal{F}_{\mathcal{R}_m}

@@

   		    	\item Reconciliation is better than no reconciliation.
